### 2015-02-11 paper/experiments.tex
fixing some issues

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{throughputvar.png}
        \caption{Throughput Variation}
        \label{throughputvar}
\end{figure}

@@

We used the same graph (Figure \ref{ecgGraph}) used in above experiment with 1,2 and 4 \textit{EventReciver} nodes with one \textit{EventSender} node for this experiment. Since 40 thread pool size and 40 message buffer size gives highest throughput, we used that values with our solution. Further we compared our system with Yahoo S4 and Twitter Storm with the same graph. Twitter Storm places tasks arbitrarily within the available nodes. Therefore we used 1 task for \textit{EventSender} and 1,2 and 4 tasks for \textit{EventReceivers} to place them in different nodes. This makes Twitter Storm execute only one thread to process data in each node. In order to compare this situation, we measured our system performance with 1 thread and 10 message buffer size as well.

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{throughput.png}
        \caption{Throughput of the systems}
        \label{throuput}
\end{figure}

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{network.png}
        \caption{Network Usage of the Systems}
        \label{networkusage}
\end{figure}

@@

As in the earlier case, we conducted our experiments using one producer and incrementing the other processing nodes by 1, 2 and 4 times to measure the throughput increase at the producer. We ran each node in a separate machine so that our receiver configurations used 5, 10, 15 machines respectively. All nodes were configured to use both thread pool and message buffer size of 40. We measured the throughput, network bandwidth and the CPU load average at the producer to examine the scalability of the system. Since the one receiver unit throughput is greater than that of the Twitter Storm one node scenario, we only used our system for this experiment. As shown in Figure \ref{scalability} system scales up until it fully utilized the available network bandwidth.

\begin{figure*}[!t]
        \centering
        \subfloat[Throughput]{\includegraphics[width=3.0in]{throughputs.png}}
        \hfil
        \subfloat[Network Usage]{\includegraphics[width=3.0in]{networkps.png}}
        \hfil
        \subfloat[Network Usage Bandwidth]{\includegraphics[width=3.0in]{networks.png}}
        \hfil
        \subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverages.png}}
        \caption{Scalability of the System}
        \label{scalability}
\end{figure*}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{allthroughput.png}
        \caption{All to All Throughput}
        \label{allthroughput}
\end{figure}

As shown in Figure \ref{allthroughput} system linearly scales with the number of nodes.  Compared to Naiad and Storm we have achieved better performance.  Figure \ref{alllatency} shows the mean message latency for all messages. We measured the message message latency during the same experiment by sending the time stamp along with each message. Compared to Storm we have achieved much lesser latency level. Naiad reports very low latency. However they do not measure the latency of the data messages in the stressed system but measure the latency of control messages.  MillWheel has reported very low latency level compared to our results. Further it is worth note that the latency can be reduced by reducing the buffer size and hence reducing the throughput. We choose 20 message buffer since it gives better throughput as well as comparable low latency.

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{alllatency.png}
        \caption{All to All Latency}
        \label{alllatency}
\end{figure}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{failure_throughput.png}
        \caption{Receiver Throughput}
        \label{rthroughput}
\end{figure}

>>>>

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{throughputvar.png}
        \caption{Throughput variation with the thread pool size and message buffer size.}
        \label{throughputvar}
\end{figure}

@@

We used the same graph (Figure \ref{ecgGraph}) used in above experiment with 1,2 and 4 \textit{EventReciver} nodes with one \textit{EventSender} node for this experiment. Since 40 thread pool size and 40 message buffer size gives highest throughput, we used that values with our solution. Further we compared our system with Yahoo S4 \cite{neumeyer2010s4} and Twitter Storm \cite{toshniwal2014storm} with the same graph. Twitter Storm \cite{toshniwal2014storm} places tasks arbitrarily within the available nodes. Therefore we used 1 task for \textit{EventSender} and 1,2 and 4 tasks for \textit{EventReceivers} to place them in different nodes. This makes Twitter Storm \cite{toshniwal2014storm} execute only one thread to process data in each node. In order to compare this situation, we measured our system performance with 1 thread and 10 message buffer size as well.

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{throughput.png}
        \caption{Throughput comparison of S4, Storm and our solution.}
        \label{throuput}
\end{figure}

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{network.png}
        \caption{Network usage at each node. For multiple receiving nodes it is the network utilization at a one node.}
        \label{networkusage}
\end{figure}

@@

As in the earlier case, we conducted our experiments using one producer and incrementing the other processing nodes by 1, 2 and 4 times to measure the throughput increase at the producer. We ran each node in a separate machine so that our receiver configurations used 5, 10, 15 machines respectively. All nodes were configured to use both thread pool and message buffer size of 40. We measured the throughput, network bandwidth and the CPU load average at the producer to examine the scalability of the system. Since the one receiver unit throughput is greater than that of the Twitter Storm \cite{toshniwal2014storm} one node scenario, we only used our system for this experiment. As shown in Figure \ref{scalability} system scales up until it fully utilized the available network bandwidth.

\begin{figure*}[!t]
        \centering
        \subfloat[Throughput of the System]{\includegraphics[width=3.0in]{throughputs.png}}
        \hfil
        \subfloat[Network Usage (\%) at Sender]{\includegraphics[width=3.0in]{networkps.png}}
        \hfil
        \subfloat[Network Usage Bandwidth at Sender]{\includegraphics[width=3.0in]{networks.png}}
        \hfil
        \subfloat[CPU Load Average at Sender]{\includegraphics[width=3.0in]{loadaverages.png}}
        \caption{Performance of Multistage Graph processing.}
        \label{scalability}
\end{figure*}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{allthroughput.png}
        \caption{All to All exchange Throughput}
        \label{allthroughput}
\end{figure}

As shown in Figure \ref{allthroughput} system linearly scales with the number of nodes.  Compared to Naiad (Figure 6(a) in cited paper) \cite{murray2013naiad} and Spark Streaming (Figure 4 in cited paper) \cite{zaharia2013discretized} we have achieved better performance.  Figure \ref{alllatency} shows the mean message latency for all messages. We measured the message latency during the same experiment by sending the time stamp along with each message. Compared to Spark Streaming (Figure 4 in cited paper) \cite{zaharia2013discretized} we have achieved much lesser latency level. Naiad (Figure 6(b) in cited paper) \cite{murray2013naiad} reports very low latency for Global barrier messages. However our latency corresponds to message latency for data messages. MillWheel (Section 8.1) \cite{akidau2013millwheel} has reported very low latency level compared to our results. Further it is worth note that the latency can be reduced by reducing the buffer size and hence reducing the throughput. We choose 20 message buffer since it gives better throughput as well as comparable low latency.

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{alllatency.png}
        \caption{All to All exchange Latency}
        \label{alllatency}
\end{figure}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{failure_throughput.png}
        \caption{Receiver throughput variation at the last node.}
        \label{rthroughput}
\end{figure}

### 2015-02-11 paper/system_architecture.tex
fixing some issues

\section{System Design}
In this section we describe key aspects of our system design which increase the throughput of inter node communication. First of all it is worth to note that even with one TCP connection, it is possible to saturate the network link usage if the sending and receiving processes send and receive byte arrays without a delay. However serializing java object messages to byte arrays and deserializing back takes considerable amount of time. Therefore we can improve the communication performance by reducing this message processing time. We use multitasking and bulk message serializing to solve this problem.

In this design, we use thread pools both at client side and server side to processes messages while sharing a single TCP connection. Firstly both thread pools access underline connection resource only to send receive byte arrays making message serialization and deserialization processes parallel. Secondly it serializes messages together to improve serialization process.  Figure \ref{interprocess} shows the design involved in sending a message from one process to another.

First the client process thread sends this message to its \textit{ElementContainer}. \textit{ElementContainer} holds all the streams (this is an abstraction of a link in the process graph) to which this message needs to be send and it pushes the message to all the streams. Stream decides the target node and buffers the messages for a configured amount of messages. Then it passes the buffered  message list along the target node details to \textit{ConnectionManager} which holds \textit{ClientConnection}s for each node. \textit{ConnectionManager} serializes the message list and sends the byte array to correct \textit{ClientConnection} using the target node. \textit{ClientConnection} uses the \textit{DataOutput} which wraps the TCP connection to send message to server side.

>>>>

\section{System Design}
In this section we describe key aspects of our system design which increase the throughput of inter node communication. First of all it is worth to note that even with one TCP connection, it is possible to saturate the network link usage, if the sending and receiving processes send and receive byte arrays without any delay even with 256 bytes array messages. However serializing java object messages to byte arrays and deserializing byte arrays back to java objects take considerable amount of time. Hence the key aspect of  improving the system performance is to reduce this message processing delay. We use multitasking and bulk message serializing to solve this problem.

In this design, we use thread pools both at client side and server side to processes messages while sharing a single TCP connection. Firstly both thread pools access underline connection resource only to send receive byte arrays making message serialization and deserialization process parallel. Secondly it serializes messages together to improve performance of the serialization process.  Figure \ref{interprocess} shows the design involved in sending a message from one process to another.

Lets assume client side process requires to send a set of messages to server side process. In order to send these messages first the client process threads send these messages to its \textit{ElementContainer}. \textit{ElementContainer} holds all the streams (this is an abstraction of a link in the process graph) to which these messages need to be send and it pushes each message to all the streams. Stream decides the target node and buffers messages for a configured amount of size. Then it passes the buffered  message list along the target node details to \textit{ConnectionManager} which holds \textit{ClientConnection}s for each node. \textit{ConnectionManager} serializes the message list and sends the byte array to correct \textit{ClientConnection} using the target node. \textit{ClientConnection} uses the \textit{DataOutput} which wraps the TCP connection to send message to server side.
